---
title: "`r read.dcf('DESCRIPTION', fields = 'Package')[1]`"  
author: "`r rworkflows::use_badges()`" 
date: "<h4>README updated: <i>`r format( Sys.Date(), '%b-%d-%Y')`</i></h4>"
output:
  github_document
---

<!-- To modify Package/Title/Description/Authors fields, edit the DESCRIPTION file -->

```{r, echo=FALSE, include=FALSE}
pkg <- read.dcf("DESCRIPTION", fields = "Package")[1]
title <- read.dcf("DESCRIPTION", fields = "Title")[1]
description <- gsub("\n"," ",read.dcf("DESCRIPTION", fields = "Description")[1])
URL <- read.dcf('DESCRIPTION', fields = 'URL')[1]
owner <- strsplit(URL,"/")[[1]][4]
repo <- strsplit(URL,"/")[[1]][5]
```

## Introduction

KGExplorer is an R package designed to facilitate seamless exploration,
manipulation, and visualization of biomedical knowledge graphs and ontologies.
By integrating robust tools for data retrieval, filtering, mapping, and graph
visualization, KGExplorer empowers researchers to work with complex biomedical
datasets from resources like the the
[Monarch Initiative](https://monarchinitiative.org) and
[Human Phenotype Ontology (HPO)](https://hpo.jax.org). With its modular design
and extensive caching support, the package streamlines workflows by reducing
redundant downloads and providing efficient tools for managing large-scale
biomedical data.

Built on the foundations of powerful R libraries like tidygraph, data.table,
ggplot2, and plotly, KGExplorer offers intuitive functions to manipulate and
visualize knowledge graphs. Researchers can subset graphs, convert between graph
representations, map between diverse ID systems, and generate interactive 3D
visualizations of ontologies. KGExplorer is tailored for biomedical researchers
seeking an efficient, flexible toolkit to harness the potential of knowledge
graphs for scientific discovery.

`KGExplorer` was developed by the [Neurogenomics
Lab](https://www.neurogenomics.co.uk/) at Imperial College London, along
with valuable feedback provided by the HPO team. This package is still
actively evolving and growing. Community engagement is welcome and any
suggestions can be submitted as an
[Issue](https://github.com/neurogenomics/KGExplorer/issues) or [Pull
Request](https://github.com/neurogenomics/KGExplorer/pulls).

## Installation 

Within R: 

```R
if(!require("remotes")) install.packages("remotes")

remotes::install_github("`r paste(owner,repo,sep='/')`")
library(`r pkg`)
```

## Documentation 

#### [Website](https://`r owner`.github.io/`r pkg`) 
#### [Get started](https://`r owner`.github.io/`r pkg`/articles/`r pkg`)
#### [Docker/Singularity Container](https://`r owner`.github.io/`r pkg`/articles/docker.html)

## Citation

If you use ``r pkg``, please cite: 

<!-- Modify this by editing the file: inst/CITATION  -->
> `r utils::citation(pkg)$textVersion`

## Contact

### [Neurogenomics Lab](https://www.neurogenomics.co.uk)   
UK Dementia Research Institute  
Department of Brain Sciences  
Faculty of Medicine  
Imperial College London  
[GitHub](https://github.com/neurogenomics)

## Session Info 

<details> 

```{r Session Info}
utils::sessionInfo()
```

</details>  
<hr>
